---
title: "Miscell"
author: "Jinshi"
date: "7/13/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
MGRsD_Q10 <- drake::readd(MGRsD_Q10)
```


## code no longer used
```{r longterm field experiment, fig.height=3, fig.width=8}
# test first site
# plot raw data vs rolling mean data
sub_data <- data.frame(x1 = sub_longterm[, 2], y1 = c(1:length(sub_longterm)))
raw_plot <- ggplot (aes(x1, y1),  data = sub_data) + geom_col() +
  scale_x_continuous(breaks = seq(0,25,5)) +
  labs(x = "Years after 1st Rs measurement", y = expression(Rs_annual~"("~g~C~m^{2}~yr^{-1}~")")) + 
  ggtitle ("(a) Raw data")

# roling mean by 3
rolingmean <- movingAverage (y1, 3)
sub_data <- data.frame(rolingmean[3:length(y1)], 1:length(rolingmean[3:length(y1)]) )
colnames(sub_data) <- c('y1', 'x1')

# lines(x1, rolingmean, col="green", lwd=2)
roling <- ggplot (aes(x1, y1),  data = sub_data) + geom_col() + 
  labs(x = "Years after 1st Rs measurement", y = expression(Rs_annual~"("~g~C~m^{2}~yr^{-1}~")")) +
  ggtitle("(b) Rolling mean of 3 yrs")

plot_grid(raw_plot, roling, ncol = 2, hjust = c(-3.25, -2.5), vjust = c(2.5, 2.5))
```


* Each site (at least 5 years continous measurement), Mann-Kendall test was used to detect the trend change
* tau > 0 means increase trend, tau > 0.184 means significant increase trend
* tau < 0 means decrease trend, tau < -0.184 means significant decrease trenc
* the results show that overall, there are no trend (tau values not significantly differ from 0)
```{r}
# Mann-Kendall test for each site and see whether the slope differ from 0
# longtern_test(longterm)
# ncol(longterm)

# var_txt <- unlist(
#   list.files(path = "~/Documents/PNNL/bigdata/UDel/Global2011T_XLS",
#   pattern = NULL,
#   all.files = FALSE,
#   full.names = FALSE,
#   recursive = TRUE,
#   ignore.case = FALSE,
#   include.dirs = FALSE)
# )
```


* Same results using data from MGRsD
* Using Rs data from MGRsD, we analyzed Rs vs. temperature in different biome for 1990s and 2000s
* How Rs response to temperature change does not shift in 2000s comparing to 1990s in most biome
```{r}
# plot Q10
MGRsD_Q10 <- MGRsD_Q10[MGRsD_Q10$Q10SY <= 10, ]
max(MGRsD_Q10$p_Q)
MGRsD_Q10 <- MGRsD_Q10[MGRsD_Q10$p_Q <= 0.1,]
MGRsD_Q10$Decades <- ifelse (MGRsD_Q10$studyYear <= 2000, '1990s', '2010s')
mean(MGRsD_Q10$Q10)
ggplot(data = MGRsD_Q10, aes(Q10SY)) + geom_histogram(fill = 'gray', col = 'black', binwidth = 0.25, alpha = 0.25)
```


* MLR model summary
```{r}
sum_MLR <- biome_MLR_MGRsD(MGRsD_sum)
print(sum_MLR)
sum_MLR <- biome_MLR_MGRsD(MGRsD)
```

* using baysian approach?
```{r, fig.width=8, fig.height=5}
plot_tfw_sft(srdb_v4, MGRsD_Q10)
```

# Distribution of Q10 (not significant)
```{r}
ggplot(MGRsD_Q10, aes(Q10SY, color = (studyYear>2000), fill = (studyYear>2000)) ) + geom_density(stat = 'density', alpha = 0.25 ) +
    ggtitle('Q10 from MGRsD: 1990s vs 2000s') +
    xlab(expression(Q[10])) +
    theme(legend.position = c(0.75,0.65),
          legend.background = element_rect(colour = 'transparent',
                                           fill = alpha('white', 0), size = 0.75) )
```

```{r}
# plot by each biome
var_biome <- sort(unique(MGRsD_Q10$MiddleClimate))
for(i in 1:length(var_biome)) {
  MGRsD_Q10_biuome <- MGRsD_Q10[MGRsD_Q10$MiddleClimate == var_biome[i],]
  p <- ggplot(MGRsD_Q10_biuome, aes(Q10SY, color = (studyYear>2000), fill = (studyYear>2000)) ) + 
    geom_density(stat = 'density', alpha = 0.25 ) +
    ggtitle(var_biome[i]) +
    xlab(expression(Q[10])) +
    theme(legend.position = c(0.75,0.65),
          legend.background = element_rect(colour = 'transparent', fill = alpha('white', 0), size = 0.75))
  print(p)}

```


* Wether the Q10 response can be detected in site scale?
** using site scale long term Rs measurement (no experiment manipulation, i.e., only control used if have warming, N-addition, CO2 increasing)
** using results from Ben's AGU present results?
```{r, fig.height = 6, fig.width = 8}
n_sample <- c(84,84,84,84,84,53,38,31,19,12)
n_study <- c(48,48,48,48,48,31,23,16,7,4)
paste0(n_sample,"/",n_study)
  
sub_longterm <- longterm[,c(1,which(colnames(longterm) == "count"), which(colnames(longterm) == "year1"): which(colnames(longterm) == "year10"))]
# temperature anomaly
sub_longterm_tm <- longterm_tm_del[,c(1,which(colnames(longterm_tm_del) == "count"),
                                   which(colnames(longterm_tm_del) == "year1"): which(colnames(longterm_tm_del) == "year10"))]

# combine two tables and plot
bind_rows(
  sub_longterm_tm %>% 
    dplyr::select(-StudyID, -count) %>% 
    tidyr::gather() %>% 
    tidyr::separate(key, c("no", "Year"), sep = "year") %>% 
    mutate(Grp = "(a) Temperature annomaly"),

  sub_longterm %>% 
    dplyr::select(-StudyID, -count) %>% 
    tidyr::gather() %>% 
    tidyr::separate(key, c("no", "Year"), sep = "year") %>% 
    mutate(Grp = "(b) Rs annomaly")) %>%
  dplyr::select(-no) %>% 
  group_by(Grp, Year) %>% 
  summarize(value = mean(value, na.rm = TRUE)) %>% 
  mutate(Year = as.numeric(Year)) %>% 
  ggplot(aes(Year, value)) +
  geom_bar(stat = "identity",
           fill = "gray",
           col = "gray",
           width = 0.65) +
  geom_smooth(method = "lm",
              se = FALSE,
              linetype = "dashed",
              col = "red") +
  facet_grid(row = vars(Grp),
             scales = "free") +
  labs(x = expression("Sample/Study"), 
       y = expression(R[S]~annomaly~(g~C~m^{2}~yr^{-1}~","~T~annomaly~(degree~C))))+
  scale_x_continuous(sec.axis=sec_axis(trans=~ ., name="Year after experiment"),
                     breaks = 1:10,
                     labels = paste0(n_sample,"/",n_study))

# another way to plot
sub_longterm %>% 
  dplyr::select(-StudyID, -count) %>% 
  tidyr::gather() %>% 
  ggplot(aes(key, value)) +
  geom_violin(fill = "skyblue") +
  scale_x_discrete(limits = c("year1","year2","year3","year4","year5","year6",
                              "year7","year8","year9","year10"),
                   labels = c(1:10)) +
  stat_summary(fun.y=median, geom="point", size=2, color="red") +
  labs(x = expression(Years~since~experiment),
       y = expression(Annual~R[S]~anomaly~(g~C~m^{-2}~yr^{-1}))) +
  ylim(-500, 800) +
  annotate("text", x=1:10, y=750, label=paste0(n_sample,"/",n_study), angle = 90)

sub_longterm_tm %>% 
  dplyr::select(-StudyID, -count) %>% 
  tidyr::gather() %>% 
  ggplot(aes(key, value)) +
  geom_violin(fill = "skyblue") +
  scale_x_discrete(limits = c("year1","year2","year3","year4","year5","year6",
                              "year7","year8","year9","year10"),
                   labels = c(1:18)) +
  stat_summary(fun.y=median, geom="point", size=2, color="red") +
  labs(x = expression(Years~since~experiment),
       y = expression(Annual~R[S]~anomaly~(g~C~m^{-2}~yr^{-1}))) 

# mann-kendall test
bind_rows(
  sub_longterm_tm %>% 
    dplyr::select(-StudyID, -count) %>% 
    tidyr::gather() %>% 
    tidyr::separate(key, c("no", "Year"), sep = "year") %>% 
    mutate(Grp = "(a) Temperature annomaly"),

  sub_longterm %>% 
    dplyr::select(-StudyID, -count) %>% 
    tidyr::gather() %>% 
    tidyr::separate(key, c("no", "Year"), sep = "year") %>% 
    mutate(Grp = "(b) Rs annomaly")) %>%
  dplyr::select(-no) %>% 
  group_by(Grp, Year) %>% 
  summarize(value = mean(value, na.rm = TRUE)) %>% 
  mutate(Year = as.numeric(Year)) %>% 
  arrange(Grp, Year) -> 
  longterm_agg

mk_tm <- MannKendall(longterm_agg$value[1:10])
mk_rs <- MannKendall(longterm_agg$value[11:20])

summary(mk_tm)
summary(mk_rs)
```


```{r}
# test Q10 by Biome
srdb_sub <- filtration (srdb_v4, 'Q10_all')
var_filt <- sort(unique(srdb_sub$Biome))
# var_filt <- var_filt[c(-3, -4, -6)]
for (i in 1:length(var_filt)) {
  srdb_biome <- srdb_sub[srdb_sub$Biome == var_filt[i], ]
  Q10_1 <- Q10_early_late (srdb_biome, 'Q10_0_10', paste0(var_filt[i]," (0-10cm)"))
  print(Q10_1)
}
```

```{r}
# test R10 by biome
srdb_sub <- filtration (srdb_v4, 'R10')
var_filt <- sort(unique(srdb_sub$Biome))
# var_filt <- var_filt[c(-3, -4, -6)]
for (i in 1:length(var_filt)) {
  srdb_biome <- srdb_sub[srdb_sub$Biome == var_filt[i], ]
  R10_early_late (srdb_biome, 'R10', var_filt[i])
}
```

* How soil respiration response to precipitation change?
* Q10 vs PDSI regression
* Results show that there are no singificant relationship between Q10 and drought (indentified by PDSI)
```{r}
Q10_pdsi(srdb_v4)
```


