---
title: "1Time_for_warm_analysis.rmd, COSORE dataset - daytime as warm treatment"
output: html_document
---

```{r preliminaries, message=TRUE, include=FALSE, echo=FALSE}
# Set chunks defaults; these options will be applied to all subsequent chunks
knitr::opts_chunk$set(results = 'hide', message = TRUE, include = TRUE, echo = FALSE,
                      fig.height = 4.5, fig.width = 8, cache = T)
# install.packages('cowplot')
# Load required packages
library(cowplot)
library(data.table)
library(ggplot2)
theme_set(theme_bw())
library(lubridate)
library(kableExtra)
library(cowplot)
library(knitr)
library("ggpubr")
library(reshape)
# install.packages('Kendall')
library(zoo)
library(Kendall)
library(dplyr)
library(tidyr)
library(lubridate)
library(maps)
library(mapdata)
# devtools::install_github("bpbond/cosore")
library(cosore)
library(lubridate)
# Source all needed functions
source('Rcode/functions.R')
source('Rcode/functions_for_cosore.R')
# Much of this was presented at AGU 2018
library(readr)
library(lattice)
library(mblm)  # for Theil-Sen robust trend test
library(grid)
library(hexbin)
```


```{r}
DATA_DIR <- 'data'
plot_dir <- "outputs/agu_slides/"
# get data
srdb_v4 <- drake::readd(srdb_v4) 
srdb_v4$Decades <- ifelse (srdb_v4$Year <= 2005, '1990s', '2010s')
srdb_v5 <- drake::readd(srdb_v5)
PT_Del <- drake::readd(PT_Del)
PT_Del$Decades <- ifelse (PT_Del$Year <= 2005, 'Early', 'Later')
MGRsD <- drake::readd(MGRsD)
MGRsD %>% 
  filter(Rs_Norm > 0 & !is.na(Rs_Norm) & !is.na(MiddleClimate)) %>% 
  mutate(RsLog = log(Rs_Norm)) ->
  MGRsD
MGRsD_q10 <- drake::readd(MGRsD_q10)
longterm <- drake::readd(longterm)
longterm_Tm <- drake::readd(longterm_Tm)
# longterm_tm_del <- drake::readd(longterm_tm_del)
# longterm_tm_del <- read_file('LongTerm_tm_del.csv')
IGBP <- read.csv("~/Documents/PNNL/SoilRespirationPartitioning/data/IGBP_Koppen_MODIS.csv")
left_join(srdb_v4, IGBP, by = c("Lat_Round" = "Latitude", "Long_Round" = "Longitude")) ->
  srdb_v4

srdb_v4 %>% 
  dplyr::select(Q10_all, MiddleClimate) %>% 
  filter(Q10_all < 10) %>% 
  na.omit() %>% 
  group_by (MiddleClimate) %>% 
  summarise(Q10_mean = mean(Q10_all), obs = n(), se = sd(Q10_all)/sqrt(obs)) ->
  srdb_v4_agg

# cosore data
cosore_all <- drake::readd(cosore_all)
cosore_q10 <- drake::readd(corsore_q10)

```



```{r}
# test calculate Q10
Q10_test_data <- tibble(CSR_TS = c(1:20),
                        Rh = 0.5*exp(log(2)/10*CSR_TS),
                        Rh_log = log(Rh))

csr_rh_Q10(Q10_test_data)

csr_database()$CSR_DATASET
csr_dataset("d20190526_PENNINGTON")
```


```{r}
colnames(cosore_q10)[2] <- "ID"

bind_rows(
  cosore_q10 %>% 
    separate(ID, c("dset", "extra"), "-", extra = "merge") %>% 
    filter(Q10_day < 10 & Q10_night < 10) %>% 
    mutate(Q10_dif = Q10_day - Q10_night,
           ST_dif = m_ts_day - m_ts_night,
           SM_dif = m_sm_day - m_sm_night) %>% 
    filter(Q10_dif > -2.5 & Q10_dif < 2.5) %>% 
    filter(ST_dif > 0.5) %>% 
    mutate(data = "Ts (day) > Ts (night)"),
  cosore_q10 %>% 
    separate(ID, c("dset", "extra"), "-", extra = "merge") %>% 
    filter(Q10_day < 10 & Q10_night < 10) %>% 
    mutate(Q10_dif = Q10_day - Q10_night,
           ST_dif = m_ts_day - m_ts_night,
           SM_dif = m_sm_day - m_sm_night) %>% 
    filter(Q10_dif > -2.5 & Q10_dif < 2.5) %>% 
    filter(ST_dif < -0.5) %>% 
    mutate(data = "Ts (day) < Ts (night)")) %>% 
  dplyr::select(dset, data, Q10_dif, ST_dif, SM_dif) %>% 
  filter(dset %!in% c("dset3", "dset6")) %>% 
  mutate(dset = factor(dset, levels=c("dset1", "dset2", "dset4", "dset5", "dset7", "dset8", "dset9", "dset10", "dset11", "dset12"))) ->
  cosore_q10_dn

cosore_q10_dn[cosore_q10_dn$dset == "dset5",] #dset5 in unit of %, need to scale it back
cosore_q10_dn[cosore_q10_dn$dset == "dset5",]$SM_dif <- cosore_q10_dn[cosore_q10_dn$dset == "dset5",]$SM_dif/100
cosore_q10_dn$SM_dif = cosore_q10_dn$SM_dif * 100 #change all to in unit of %

cosore_q10_dn %>% 
  gather(-dset, -data, key = "Factors", value = "dif") %>% 
  ggplot(aes(dset, dif, fill = dset)) +
  geom_violin() +
  geom_hline(yintercept = 0, linetype = 2, col = "red") +
  facet_grid(cols = vars(data), rows = vars(Factors), scales = "free") 
 
```

```{r, fig.width=8, fig.height=7}
cosore_q10_dn %>% 
  ggplot(aes(dset, Q10_dif, fill = dset)) +
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75)) +
  geom_hline(yintercept = 0, linetype = 2, col = "red") +
  facet_grid(cols = vars(data)) +
  labs(y = expression(Day - night~Q[10])) +
  theme(axis.title.x = element_blank(),
        axis.ticks = element_blank(),
        axis.text.x = element_blank(),
        legend.position = "none",
        axis.title.y = element_text(margin = margin(t = 0, r = 10, b = 0, l = 0))) ->
  plot_q10_dif
  

cosore_q10_dn %>% 
  ggplot(aes(dset, ST_dif, fill = dset)) +
  geom_boxplot(outlier.size=-1) +
  geom_hline(yintercept = 0, linetype = 2, col = "red") +
  facet_grid(cols = vars(data)) +
  labs(y = expression(Day - night~T[soil]~(degree~C))) +
  theme(axis.title.x = element_blank(),
        axis.ticks = element_blank(),
        axis.text.x = element_blank(),
        legend.position = "none") ->
  plot_ts_dif

cosore_q10_dn %>% 
  ggplot(aes(dset, SM_dif, fill = dset)) +
  geom_boxplot(outlier.size=-1) +
  geom_hline(yintercept = 0, linetype = 2, col = "red") +
  facet_grid(cols = vars(data)) +
  labs(x = "Data set",
       y = expression(Day - night~SM~('%'))) +
  scale_y_continuous(limits = c(-1.5, 1.5)) +
  scale_x_discrete(labels=c("dset1" = "ds1",
                            "dset2" = "ds2",
                            "dset4" = "ds3",
                            "dset5" = "ds4",
                            "dset7" = "ds5",
                            "dset8" = "ds6",
                            "dset9" = "ds7",
                            "dset10" = "ds8",
                            "dset11" = "ds9",
                            "dset12" = "ds10")) +
  theme(legend.position = "none") ->
  plot_sm_dif

plot_grid(plot_q10_dif, plot_ts_dif, plot_sm_dif,
          labels = c("a", "b", "c"),
          rel_heights = c(1,1,1.2),
          ncol = 1)
```


## Find long term (n>5) studies from srdb-v5
```{r find out longterm studies from srdb}
# get study number from srdb_v5 which have more than 5 years of Rs measurement
# 10977 can be read from the fiture
study_exc <- c(6935,4174,3301,3302,3254,3197,6347,4864,3581,5935,
               2927,1654,5278,6451,4333,4564,4938,5519,6504,2656,
               7290,7636,10266,2298,
               # already in the longterm data
  
               # checked in srdb and mgrsd
               467,864,1980,2018,2601,2926,2960,
               3390,4212,4234,4270,4979,5545,5984,6816,7087,
               7613,8699,8700,9845,10449,10624,10820,10951,10977,11054,11913,
               # checked github issue
               4333,4348,10614,10466,11054,
               # checked srdb by study_number and site_id
               1891,2056,2904,3053,4018,4442,4894,5162,5688,6438,6975,7634,8479,
               8534,10066,10483,10564,10910,11366)
srdb_v5 %>% 
  filter(!is.na(Rs_annual)) %>% 
  dplyr::select(Rs_annual, Study_number, YearsOfData) %>% 
  count(Study_number, YearsOfData) %>% 
  filter(YearsOfData>=5 & Study_number %!in% study_exc)

srdb_v5 %>% 
  filter(!is.na(Rs_annual)) %>% 
  dplyr::select(Rs_annual, Study_number, Site_ID) %>% 
  count(Study_number, Site_ID) %>% 
  filter(Study_number %!in% study_exc) %>% 
  filter(n > 4)
```

## Plot long term sites spatial distribution
```{r site map, fig.height = 4, fig.width = 8}
# plot a site map for the long term data collected
# Step 2: Plot
# sort(unique(counties$region))
csr_database() %>% 
    filter(grepl('Rh', CSR_MSMT_VAR)) %>% 
    mutate(Latitude = CSR_LATITUDE,
           Longitude = CSR_LONGITUDE,
           count = year(CSR_DATE_END) - year(CSR_DATE_BEGIN),
           Data = "COSORE") %>% 
    select(Latitude, Longitude, count, Data) ->
  csr_rh_site

bind_rows(
  MGRsD %>% 
    filter(!is.na(Rs_Norm)) %>% 
    select(Latitude, Longitude, Meas_Year, Study_number) %>% 
    unique() %>% 
    group_by(Latitude, Longitude) %>% 
    summarise(count = n()) %>% 
    select(Latitude, Longitude, count) %>% 
    mutate(Data = "DGRsD"),
  
  srdb_v4 %>% 
    filter(!is.na(Q10_all) & !is.na(Latitude)) %>% 
    mutate(Meas_Year = Study_midyear) %>% 
    select(Latitude, Longitude, Meas_Year, Study_number) %>% 
    unique() %>% 
    group_by(Latitude, Longitude) %>% 
    summarise(count = n()) %>% 
    select(Latitude, Longitude, count) %>% 
    mutate(Data = "SRDB"),
  
  csr_rh_site,
  
  longterm %>% 
    select(Latitude, Longitude, count) %>% 
    mutate(Data = "Long-term")) ->
  map_sites


ggplot(data = map_data("world", region = ".", exact = FALSE)) + 
  geom_polygon(aes(x = long, y = lat, group = group),
               color = "white", fill = 'gray') + 
  guides(fill=FALSE) +
  geom_point(data = map_sites,
             aes(x=Longitude, y=Latitude,
                 size = count,
                 col = Data,
                 shape = Data),
             stroke = 1,
             alpha = 0.75) +
  geom_point(data = csr_rh_site,
    aes(x=Longitude, y=Latitude, size = count),
    col = "#F8766D", alpha = 0.75) +
  scale_shape_manual(values = c(16, 17, 1, 4)) +
  scale_x_continuous(name="Longitude", breaks=seq(-180,180, 60),labels = seq(-180,180, 60))+
  scale_y_continuous(limits = c(-60, 90),name="Latitude", breaks=seq(-60,90,30),labels = seq(-60,90,30)) +
  scale_size_continuous(name = "Years (n)") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank())
```

```{r, fig.height=6, fig.width=6}
# get the percentage of early period to total
early_perc <- function(var_year) {
  MGRsD %>% 
    select(Meas_Year, Rs_Norm) %>% 
    na.omit() %>% 
    filter(Meas_Year <= var_year) %>% 
    nrow() ->
    output
  return (output)
}

MGRsD %>% 
  select(Meas_Year, Rs_Norm) %>% 
  na.omit() %>% 
  # group_by(Meas_Year) %>% 
  # summarise(obs = n(), Rs_mean = mean(Rs_Norm), Rs_sd = sd(Rs_Norm)) %>% 
  ggplot(aes(x = Meas_Year, y = Rs_Norm)) +
  geom_hex(col = "gray", bins = 35) +
  scale_fill_distiller(palette = "YlGnBu", name = "Count", direction = -1) +
  scale_x_continuous(breaks=seq(1960, 2017, 10)) +
  theme(axis.title.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        legend.position = c(0.25, 0.70)) +
  labs(y = expression(R[S]~(g~C~m^{-2}~day^{-1}))) ->
  panel_a

# 1990 - 2009
tibble(ct_start = rep(1961, 20), ct_end = c(2009:1990),
       wm_start = c(2010:1991), wm_end = rep(2017, 20)) ->
  arrow_data

tibble(year = c(1960:2017), intc = runif(58, min=0, max=21)) %>% 
  ggplot(aes(x = year, y = intc)) +
  geom_segment(aes(x = ct_start, y = c(1:20), xend = ct_end, yend = c(1:20)),
               arrow = arrow(length = unit(0.25, "cm")),
               size = 0.25,
               col = "blue",
               data = arrow_data) +
  geom_segment(aes(x = wm_start, y = c(1:20), xend = wm_end, yend = c(1:20)),
               arrow = arrow(length = unit(0.25, "cm")),
               size = 0.25,
               col = "red",
               data = arrow_data) +
  # make 50% bold
  geom_segment(aes(x = 1961, y = 5, xend = 2005, yend = 5),
               arrow = arrow(length = unit(0.25, "cm")),
               size = 0.5,
               col = "blue") +
  geom_segment(aes(x = 2006, y = 5, xend = 2017, yend = 5),
               arrow = arrow(length = unit(0.25, "cm")),
               size = 0.5,
               col = "red") +
  scale_x_continuous(breaks=seq(1960, 2017, 10)) +
  theme(axis.title.x = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank()) +
  scale_y_continuous(breaks = c(1, 5, 10, 15, 20),
                     labels = c(round(early_perc(2009)/36165*100),
                                round(early_perc(2005)/36165*100),
                                round(early_perc(2001)/36165*100),
                                round(early_perc(1994)/36165*100),
                                round(early_perc(1989)/36165*100) )) +
  labs(y = expression(Percentage~of~R[S]~from~early~'(%)')) ->
  panel_b

plot_grid(panel_a, panel_b,
          ncol = 1,
          labels = c("a", "b"))

round(early_perc(1990)/36165*100)
round(early_perc(1994)/36165*100)
round(early_perc(1999)/36165*100)
round(early_perc(2004)/36165*100)
round(early_perc(2005)/36165*100)
round(early_perc(2006)/36165*100)
round(early_perc(2009)/36165*100)

```

* We compared mean annual air temperature bwtween 1964 and 2000 (1990s) vs. mean air temperature between 2001 and 2017 (2000s)
* Air temperature of 1990s (1964-2000) are about 0.5 C lower than that from 2000s(2001-2017)
* In boreal and polar regions, the temperature difference is bigger (difference ~~ 1 C)
* Therefore, 1990s are treated as control, 2000s are treated as warming period
```{r}
# temperature of 1990s vs 2010s
ggplot(PT_Del, aes(Decades,  Tm)) +   
  geom_boxplot()+
  facet_wrap(~MiddleClimate, nrow = 2,scales = "free")+ 
  labs(y=expression("Air temperature "*"("*degree~C*")"))
```

```{r, fig.width=8, fig.height=6}
# temperature annomaly time series
PT_Del %>% 
  ggplot(aes(Year, Tm_Annomaly)) +
  geom_bar(stat = "identity", alpha = 0.85, fill = "white", color = "black") +
  geom_smooth(color = "red", method = "lm", se = FALSE) +
  geom_smooth(color = "blue", method = "loess", se = FALSE, linetype = 2) +
  facet_wrap(~MiddleClimate, nrow = 4, scales = "free") +
  labs(x = "Year (1961-2014)", 
       y = expression(T[Air]~anomaly~(degree~C)))
# ggsave("outputs/FigureSX. T anomaly.jpg", width = 8, height = 6, dpi = 300, units = "in")
```


* We used data from both srdb_v4 and MGRsD 
* For data from MGRsD, only sites with more than 7 months' Rs measurements were used
* For each sites, we simulate the ewlationshio between Rs and Tm (air temperature) with Rs=axexp^bxTm
* According to parameter b, we can calculate Q10=exp(b*10) 

* Q10 does not show a clear trend when changing from warm biome to cold biome (negative relationship between Q10 and annual mean temperature, Space for time)
* Q10 of 1990s does not signifficantly differ from Q10 of 2010s (Time for warming, panel b and d represent data from srdb_v4 and MGRsD respectively)

* Why we see a clear Q10 decrease as annual temperature decrease, but cannot see the difference between 1990s and 2000s?
* (1) The temperature change is small, the soil respiration response (Q10) is too small to detect.
* (2) Hypothesis: some sites Q10 increase, site sites Q10 decrease, depend on ... ...
* As we seperate by biome region, we do see Q10 increased in arctic and boreal, but no change in other regions.

```{r, fig.width=8, fig.height=6}
# Q10 of 1990s and 2010s comparison by Biome
srdb_v4 %>% 
  filter(Q10_all < 10 & !is.na(Decades) & !is.na(MiddleClimate)) %>% 
  ggplot(aes(Decades, Q10_all, fill = Decades)) + 
  geom_jitter( position = position_jitter(0.2), col = 'gray' ) + 
  geom_violin(draw_quantiles = c(0.25, 0.5, 0.75), alpha = 0.5) +
  facet_wrap (~MiddleClimate, ncol = 2) +
  labs(x = "Period", y = expression(Q[10])) +
  scale_x_discrete(labels=c("1990s" = "1960-2000", "2010s" = "2001-2017")) +
  theme(legend.position = "none")
```

```{r, fig.height=6, fig.width=8}
# srdb Q10 plot
srdb_v4 %>% 
  filter(Q10_all < 10 & !is.na(Study_midyear) & !is.na(MiddleClimate)) %>% 
  dplyr::select(Q10_all, Study_midyear, MiddleClimate) %>% 
  group_by(Study_midyear, MiddleClimate) %>% 
  summarise(Q10 = mean(Q10_all), Q10_sd = sd(Q10_all), obs = n()) ->
  srdb_q10_sum 

# function for lm between Q10 and year
lm(Q10 ~ Study_midyear, data = subset(srdb_q10_sum, MiddleClimate == "A"), weights = obs) %>% summary()
lm(Q10 ~ Study_midyear, data = subset(srdb_q10_sum, MiddleClimate == "B"), weights = obs) %>% summary()
lm(Q10 ~ Study_midyear, data = subset(srdb_q10_sum, MiddleClimate == "Cf"), weights = obs) %>% summary()
lm(Q10 ~ Study_midyear, data = subset(srdb_q10_sum, MiddleClimate == "Cs"), weights = obs) %>% summary()
lm(Q10 ~ Study_midyear, data = subset(srdb_q10_sum, MiddleClimate == "Cw"), weights = obs) %>% summary()
lm(Q10 ~ Study_midyear, data = subset(srdb_q10_sum, MiddleClimate == "Df"), weights = obs) %>% summary()
lm(Q10 ~ Study_midyear, data = subset(srdb_q10_sum, MiddleClimate == "Dsw"), weights = obs) %>% summary()
lm(Q10 ~ Study_midyear, data = subset(srdb_q10_sum, MiddleClimate == "E" & Q10 < 7.5 & Study_midyear > 1990), weights = obs) %>% summary()

srdb_q10_sum %>% 
  ggplot(aes(Study_midyear, Q10)) + 
  geom_point(aes(size = obs), alpha = 0.5) + 
  geom_smooth(method = "lm", fill = "skyblue", col = "blue", data = subset(srdb_q10_sum, MiddleClimate %in% c("B", "Cf"))) +
  geom_smooth(method = "lm", fill = "pink", col = "red", data = subset(srdb_q10_sum, MiddleClimate %in% c("Df", "E"))) +
  facet_wrap (~MiddleClimate, ncol = 2) +
  labs(x=expression(Measure~year), y = expression(Q[10])) +
  labs(size="obs (n)")

```

```{r, fig.height=4, fig.width=8}
# plot space for time
plot_grid(
  srdb_v4_agg %>% 
    ggplot(aes(MiddleClimate, Q10_mean)) +
    geom_bar(stat = "identity", col = "black", fill = "white", width = 0.75) +
    geom_errorbar(aes(ymin=Q10_mean - se, ymax = Q10_mean + se), col = "black", width = 0.05) +
    coord_cartesian(ylim = c(0, 4.1)) +
    annotate("text", x = c(1:8), y = 3.75, label = paste0("n=",srdb_v4_agg$obs), angle = 90) +
    labs(x=expression(Climate~region),
         y=expression(Q[10])),
  
  srdb_v4 %>% 
    filter(Q10_all < 10 & !is.na(Q10_all) & !is.na(TAnnual_Del)) %>% 
    dplyr::select(Q10_all, TAnnual_Del) %>% 
    mutate(TAnnual_Del = round(TAnnual_Del*8)/8) %>% 
    group_by(TAnnual_Del) %>% 
    summarise(Q10_all = mean(Q10_all),
              obs = n()) %>% 
    ggplot(aes(TAnnual_Del, Q10_all, size = obs)) +
    geom_point(alpha = 0.5) +
    geom_smooth(method = "lm", show.legend = FALSE) +
    coord_cartesian(ylim = c(0, 7.5)) + 
    labs(x=expression(Annual~mean~air~temperature~(degree~C)),
         y=expression(Q[10])) +
    theme(legend.position = c(0.75, 0.8))
)

```

```{r, fig.width=8, fig.height=6}
srdb_v4 %>% 
  filter(Q10_all < 10 & !is.na(Q10_all) & !is.na(PAnnual_Del) & !is.na(MiddleClimate)) %>% 
  dplyr::select(Q10_all, PAnnual_Del, MiddleClimate) %>% 
  mutate(PAnnual_Del = round(PAnnual_Del*8)/8) %>% 
  group_by(PAnnual_Del, MiddleClimate) %>% 
  summarise(Q10_all = mean(Q10_all),
            obs = n()) ->
  srdb_q10_map_sum

# function for lm between Q10 and year
lm(Q10_all ~ PAnnual_Del, data = subset(srdb_q10_map_sum, MiddleClimate == "A"), weights = obs) %>% summary()
lm(Q10_all ~ PAnnual_Del, data = subset(srdb_q10_map_sum, MiddleClimate == "B"), weights = obs) %>% summary()
lm(Q10_all ~ PAnnual_Del, data = subset(srdb_q10_map_sum, MiddleClimate == "Cf"), weights = obs) %>% summary()
lm(Q10_all ~ PAnnual_Del, data = subset(srdb_q10_map_sum, MiddleClimate == "Cs"), weights = obs) %>% summary()
lm(Q10_all ~ PAnnual_Del, data = subset(srdb_q10_map_sum, MiddleClimate == "Cw"), weights = obs) %>% summary()
lm(Q10_all ~ PAnnual_Del, data = subset(srdb_q10_map_sum, MiddleClimate == "Df"), weights = obs) %>% summary()
lm(Q10_all ~ PAnnual_Del, data = subset(srdb_q10_map_sum, MiddleClimate == "Dsw"), weights = obs) %>% summary()
lm(Q10_all ~ PAnnual_Del, data = subset(srdb_q10_map_sum, MiddleClimate == "E"), weights = obs) %>% summary()

srdb_q10_map_sum %>% 
  ggplot(aes(PAnnual_Del, Q10_all, size = obs)) +
  geom_point(alpha = 0.5) +
  geom_smooth(method = "lm", fill = "skyblue", col = "blue", data = subset(srdb_q10_map_sum, MiddleClimate %in% c("Cf")), show.legend = FALSE) +
  geom_smooth(method = "lm", fill = "pink", col = "red", data = subset(srdb_q10_map_sum, MiddleClimate %in% c("Cs", "Dsw")), show.legend = FALSE) +
  coord_cartesian(ylim = c(0, 7.5)) + 
  labs(x=expression(Annual~precipitation~(mm)),
       y=expression(Q[10])) +
  facet_wrap(~MiddleClimate, ncol = 2)
```


## MLR of MGRsD
```{r, include=FALSE}
# biome_MLR_srdb (srdb_v4)
outputs <- biome_MLR_MGRsD_weight (MGRsD, 1990)
for (i in 1991:2009){
  outputs <- bind_rows(outputs, biome_MLR_MGRsD_weight (MGRsD, i))
  print(paste0("*****", i))
} 
```

## plot out the reuslts

```{r, fig.height = 4, fig.width = 6}
bind_rows(
  outputs %>% mutate(data = "(a) all data"),
  outputs %>% 
    filter(p_inter <= 0.05, p_tm <= 0.05) %>% 
    filter(Q10_CT >= 1 & Q10_WM >= 1) %>% 
    mutate(data = "(b) p < 0.05")) %>% 
  mutate(Q10_dif = Q10_WM - Q10_CT) %>% 
  ggplot(aes(Biome, Q10_dif)) +
  geom_hline(yintercept = 0, linetype = 2, col = "red") + 
  # geom_violin(draw_quantiles = c(0.25, 0.5, 0.75)) +
  geom_boxplot(outlier.size = 2, outlier.shape = 16,
               lwd = 0.5, width = 0.5, alpha=1, fatten = NULL,
               fill = "orange", col = "orange") +
  stat_summary(fun.y=mean, geom="point", shape=16, size=4.5, col = "gray") +
  stat_summary(fun.y=mean, geom="point", shape=16, size=1.5, col = "white") +
  labs(y = expression(Q[10]~(later)~"-"~Q[10]~(early))) +
  facet_grid(cols = vars(data)) 
```



```{r, fig.height = 6, fig.width = 8}
bind_rows(
  outputs %>% mutate(data = "(a) all data"),
  outputs %>% 
    filter(p_inter <= 0.05, p_tm <= 0.05) %>% 
    filter(Q10_CT >= 1 & Q10_WM >= 1) %>% 
    mutate(data = "(b) p < 0.05")) %>% 
  mutate(Q10_dif = Q10_WM - Q10_CT) %>% 
  ggplot(aes(Biome, Q10_dif, fill = Biome)) +
  geom_hline(yintercept = 0, linetype = 2, col = "red") + 
  # geom_violin(draw_quantiles = c(0.25, 0.5, 0.75)) +
  geom_boxplot(outlier.size = 2, outlier.shape = 16,
               lwd = 0.5, width = 0.25, alpha=0.1) +
  labs(y = expression(Q[10]~(later)~"-"~Q[10]~(early))) +
  facet_grid(rows = vars(data)) +
  scale_fill_discrete(labels = c("A-Tropic", "B-Arid", "Cf-Temperate humid", "Cs-Temperate summer dry",
                                 "Cw-Temperature winter dry", "Df-Boreal humid", "Dsw-Boreal dry", "E-Arctic"))

outputs %>% 
  filter(Biome %in% c("Dsw") & Q10_WM > Q10_CT) 

outputs %>% 
  filter(Biome %in% c("A")) 

# prepare Table S1
MGRsD$Decades <- ifelse (MGRsD$Meas_Year <= 2005, 'Early', 'Later')

bind_rows(
  outputs %>% 
    filter(B_YR == 2005),
  biome_MLR_MGRsD_all(MGRsD)
)


```


* Using SRDB_V4 (Q10 from soil temperature, Q10 are directly collected from publication)
```{r Q10 test, fig.height=6, fig.width=8}
# compare Q10 of 1961-1990 (30 years) vs 1991-2014
# colnames(srdb_v4)
Q10_1 <- Q10_early_late (srdb_v4, 'Q10_0_10', ' A (0-10 cm) ')
Q10_2 <- Q10_early_late (srdb_v4, 'Q10_5_15', ' B (5-15 cm) ')
Q10_3 <- Q10_early_late (srdb_v4, 'Q10_10_20', ' C (10-20 cm) ')
Q10_4 <- Q10_early_late (srdb_v4, 'Q10_0_20', ' D (0-20 cm) ')

plot_grid (Q10_1, Q10_2, Q10_3, Q10_4, ncol = 2)  

Q10_early_late (srdb_v4, 'Q10_all', 'All') %>% 
  print()

# bootstrap and compare mean Q10
set.seed(20200610)
RESAMPLE <- function(n, x) { # no errors/sd inputs
  mean(sample(x, n, replace = TRUE))
}

srdb_v4 %>% 
  mutate(Q10_0_20 = coalesce(Q10_0_10, Q10_0_20),
         Q10_other = coalesce(Q10_5_15, Q10_10_20, Q10_other1, Q10_other2)) %>% 
  dplyr::select(Decades, Q10_0_20, Q10_other) %>% 
  tidyr::gather(-Decades, key = "Depth", value = "Q10") %>% 
  filter(!is.na(Q10)) ->
  Q10_decades

Q10_decades %>% 
  filter(Decades == "1990s" & Depth == "Q10_0_20") ->
  Q10_1990s_0_20

Q10_decades %>% 
  filter(Decades == "2010s" & Depth == "Q10_0_20") ->
  Q10_2010s_0_20

Q10_decades %>% 
  filter(Decades == "1990s" & Depth == "Q10_other") ->
  Q10_1990s_other

Q10_decades %>% 
  filter(Decades == "1990s" & Depth == "Q10_other") ->
  Q10_2010s_other
  
bootstrap_Q10_period <- tibble(
  Q10_0_20_early = sapply(rep(20, 5000), RESAMPLE, Q10_1990s_0_20$Q10),
  Q10_0_20_later = sapply(rep(20, 5000), RESAMPLE, Q10_2010s_0_20$Q10),
  Q10_other_early = sapply(rep(20, 5000), RESAMPLE, Q10_1990s_other$Q10),
  Q10_other_later = sapply(rep(20, 5000), RESAMPLE, Q10_2010s_other$Q10)
)

bootstrap_Q10_period %>%
  tidyr::gather(key = "Group", value = "Q10") %>% 
  ggplot(aes(Q10, fill = Group)) +
  # theme_cowplot() +
  geom_density(stat = "density", alpha = 0.65) +
  theme(legend.position = c(0.80, 0.75)) 
```

```{r R10 test}
# test Q10 under Ra and Rh dominant sites
R10_early_late (srdb_v4, 'R10', 'Test R10 for early and late years')
```


* Using SPI to detect temporal trend of precipitation?
* And then see whether Q10 values have relationship with SPI trend?
* Q10 vs SPI tau values ?
* First, need get global MK test and get tau value for each site
* Second, see how Q10 differ among different tau range () ?


```{r, fig.height=8, fig.width=8}
MGRsD %>% 
  mutate(Tm_de = round(Tm_del*8)/8) %>%
  mutate(Period = case_when(
    Meas_Year <= 2005 ~ "Early",
    TRUE ~ "Later" )) %>% 
  dplyr::select(Tm_del, RsLog, MiddleClimate, Period) %>% 
  group_by(MiddleClimate, Period, Tm_del) %>% 
  summarise(RsLog = mean(RsLog),
            obs = n()) ->
  MGRsD_sum

MGRsD_sum$obs <- ifelse(MGRsD_sum$obs >= 100, 100, MGRsD_sum$obs)

MGRsD_sum %>% 
  ggplot (aes(Tm_del, RsLog, colour = Period)) +
  geom_point(aes(size = obs), alpha = 0.15) + 
  geom_smooth(method = 'lm') +
  facet_wrap(~MiddleClimate, ncol = 2) + 
  labs( y = expression(R[S]~","~log~(g~C~m^{-2}~day^{-1}) ),
        x = expression(Air~temperature~(degree~C) ) ) +
  theme(legend.position = 'top')
  
# ggsave("outputs/FigureX. MGRsD_1990svs2000s.jpg", width = 8, height = 8, dpi = 300, units = "in")
```

## Using srdb data
```{r}
srdb_biome_comparisom (srdb_v4)
```


* **Minutes to hours to days**: how frequently do we need to sample? Uses GCREW continuous data. How frequently do we need to sample?
* **Days to months**: how frequently do we need to sample for annual flux? Uses SERC survey data.
* **Years**: how much coverage is needed for robust annual estimate? This uses `Annual_coverage` field of SRDB. Not clear about this one.
* **Error introduced by RH versus RS**. Uses SRDB. Not sure about this. Hard.
* - our Nature anlysis assumed no measurement error. How could this be estimated?
* Random measurement error: "Random errors show up as different results for ostensibly the same repeated measurement. They can be estimated by comparing multiple measurements, and reduced by averaging multiple measurements." https://en.wikipedia.org/wiki/Observational_error#Random_errors_versus_systematic_errors
* - _continuous_ data: variability between measurement 1 and measurement 2
* - _survey_ (discontinuous) data: variability between m1 and m2 PLUS sampling error (sampling from continuous annual data)
* **Years to decades**: how well can we detect trends? This is Nature paper SI work.

### What's the SRDB interannual variability?
```{r srdb, echo=FALSE}
srdb_v5$Rs_interann_cv <- with(srdb_v5, Rs_interann_err / Rs_annual)
median_interann_cv <- median(srdb_v5$Rs_interann_cv, na.rm = TRUE)

srdb_v5 %>% 
  filter(!is.na(Rs_interann_cv)) %>% 
  ggplot(aes(x = Rs_interann_cv)) + 
  geom_histogram(bins = 30, fill = 'gray', col = "black") +
  scale_x_continuous(labels = scales::percent, limits = c(0, 1)) +
  geom_vline(xintercept = median_interann_cv, color = "red") +
  ylab("Count") + 
  xlab("CV between successive years") ->
  plot_annual_cv
  
# save_agu_plot("srdb_cv.png")

# Site records
srdb_v5 %>% 
  filter(!is.na(Longitude), !is.na(Rs_annual), Manipulation == "None") %>% 
  mutate(lon = round(Longitude, 2), lat = round(Latitude, 2)) ->
  srdb

# Site records
srdb %>% 
  filter(!is.na(Longitude), !is.na(Rs_annual), Manipulation == "None") %>% 
  mutate(lon = round(Longitude, 2), lat = round(Latitude, 2)) %>% 
  # Compute the longest records
  group_by(lon, lat, Leaf_habit, Ecosystem_type) %>% 
  summarise(Years = length(unique(Study_midyear))) %>% ungroup %>% 
  arrange(desc(Years)) %>% 
  top_n(10) %>% 
  left_join(dplyr::select(srdb, Site_name, lon, lat, Ecosystem_type, Study_midyear, YearsOfData),
            by = c("lon", "lat", "Ecosystem_type")) %>% 
  mutate(Site_name = substr(Site_name, 1, 10)) ->
  site_smry

ggplot(site_smry, aes(Study_midyear, Site_name, 
                      color = paste(Leaf_habit, Ecosystem_type))) + 
  geom_point() + xlab("Year") + ylab("") + scale_color_discrete("")
# save_agu_plot("site_records.png", width = 8, height = 4)
```

### What's the CV between survey measurements 1 and 2?

```{r cv12, echo = FALSE}
cosore_all %>% 
  mutate(ID_day = paste0(dset, "-", CSR_PORT, "-", year(CSR_TIMESTAMP_END),"-", month(CSR_TIMESTAMP_END), "-", day(CSR_TIMESTAMP_END))) %>% 
  group_by(ID_day) %>%
  summarise(n = n(), meanFlux = mean(CSR_FLUX_CO2), cv = sd(CSR_FLUX_CO2) / mean(CSR_FLUX_CO2)) %>% 
  filter(n >= 2) ->
  meas_error_1
median_error <- median(meas_error_1$cv)

ggplot(meas_error_1, aes(x = cv)) + 
  geom_histogram(bins = 30, fill = "gray", col = "black") +
  scale_x_continuous(labels = scales::percent, limits = c(-0.1, 1)) +
  geom_vline(xintercept = median_error, color = "red") +
  ylab("Count") + 
  xlab("CV between successive IRGA measurements") ->
  plot_IRGA_cv
# save_agu_plot("licor12_cv.png")
```

OK, so the median measurement error here is ~`r round(median_error * 100, 0)`% for `r nrow(meas_error_1)` observations of fluxes between `r round(min(meas_error_1$meanFlux), 2)` and `r round(max(meas_error_1$meanFlux), 2)` µmol/m2/s.

### Nature paper analysis
```{r hashimoto, echo=FALSE}
library(ncdf4)
# Downloaded August 25, 2017 from http://cse.ffpri.affrc.go.jp/shojih/data/index.html
ncfiles <- c("~/Data/Hashimoto/RH_yr_Hashimoto2015.nc",
             "~/Data/Hashimoto/RS_yr_Hashimoto2015.nc")

nc <- nc_open(ncfiles[1])
# These annual data start in 1901; extract 1990-2012
co2 <- ncvar_get(nc, "co2", start = c(1, 1, 1, 90), count = c(-1, -1, 1, 23))
nc_close(nc)


png(file.path(plot_dir, "co2.png"))
lattice::levelplot(co2[,,1])
dev.off()

co2 <- co2[400:600, 220:360,]  # punch a hole for testing: North America
#co2 <- co2[500:540, 320:360,]  # punch a hole for testing: part of North America

do_fitting <- function(co2) {
  
  f <- function(rh) { 
    df <- data.frame(x = seq_along(rh), y = rh)
    tryCatch(lm(y ~ x, data = df), error = function(e) NA)
  }
  
  # Fit linear model to each grid cell (this is slow)
  mods <- apply(co2, c(1, 2), FUN = f)  # slow
  
  # Extract slopes
  slopes <- apply(mods, c(1, 2), FUN = function(x) 
    if(!is.na(x)) x[[1]]$coefficients[["x"]] else NA)
  slopes <- matrix(slopes, nrow = nrow(mods), ncol = ncol(mods))
  
  # Extract slope p-values
  signif <- apply(mods, c(1, 2), FUN = function(x) 
    if(!is.na(x)) summary(x[[1]])$coefficients["x", "Pr(>|t|)"] else NA)
  signif <- matrix(signif, nrow = nrow(mods), ncol = ncol(mods))
  
  return(list(slopes = slopes, signif = signif))
}

out <- do_fitting(co2)
summary(as.vector(out$slopes))

png(file.path(plot_dir, "co2-slopes.png"))
lattice::levelplot(out$slopes > 0)
dev.off()
png(file.path(plot_dir, "co2-signif.png"))
lattice::levelplot(out$signif < 0.05)
dev.off()

ncells <- sum(!is.na(out$slopes))
pos_slope <- sum(out$slopes > 0, na.rm = TRUE)
signif_pos_slope <- sum(out$slopes > 0 & out$signif < 0.05, na.rm = TRUE)

lat_weight <- abs(cos(seq(-pi/2, pi/2, length.out = nrow(out$slopes))))
ncells_areawt <- sum(lat_weight * ncol(out$slopes))
pos_slope_areawt <- sum(out$slopes > 0 * lat_weight, na.rm = TRUE)
signif_pos_slope_areawt <- sum(out$slopes > 0 & out$signif < 0.05 * lat_weight, na.rm = TRUE)

# plot histgram
tibble(signif = as.vector(unlist(out$signif))) %>% 
  na.omit() %>% 
  ggplot(aes(x = signif)) + 
  geom_histogram(bins = 30, fill = "gray", col = "black") +
  # geom_vline(xintercept = 0.05, color = "red") +
  ylab("Count") + 
  xlab("p value of time series trend") ->
  plot_signif_before
```

Total cells = `r ncells`.

Cells with positive slope = `r pos_slope` or `r round(pos_slope / ncells * 100, 0)`%.

Cells with _significant_ positive slope = `r signif_pos_slope` or `r round(signif_pos_slope / ncells * 100, 0)`%.

Area with positive slope = `r round(pos_slope_areawt / ncells_areawt * 100, 0)`%.

Area with _significant_ positive slope = `r round(signif_pos_slope_areawt / ncells_areawt * 100, 0)`%.

### Re-do analysis with assumed error rate
```{r fuzz, echo=FALSE}

co2_fuzz <- fuzz(co2, error = median_error)
out_fuzz <- do_fitting(co2_fuzz)

png(file.path(plot_dir, "co2-fuzz-slopes.png"))
lattice::levelplot(out_fuzz$slopes > 0)
dev.off()
png(file.path(plot_dir, "co2-fuzz-signif.png"))
lattice::levelplot(out_fuzz$signif < 0.05)
dev.off()

# plot histgram after cv added
tibble(signif = as.vector(unlist(out_fuzz$signif))) %>% 
  na.omit() %>% 
  ggplot(aes(x = signif)) + 
  geom_histogram(bins = 30, fill = "gray", col = "black") +
  # geom_vline(xintercept = 0.05, color = "red") +
  ylab("Count") + 
  xlab("p value of time series trend") ->
  plot_signif_after

ncells <- sum(!is.na(out_fuzz$slopes))
pos_slope <- sum(out_fuzz$slopes > 0, na.rm = TRUE)
signif_pos_slope <- sum(out_fuzz$slopes > 0 & out_fuzz$signif < 0.05, na.rm = TRUE)

lat_weight <- abs(cos(seq(-pi/2, pi/2, length.out_fuzz = nrow(out_fuzz$slopes))))
ncells_areawt <- sum(lat_weight * ncol(out_fuzz$slopes))
pos_slope_areawt <- sum(out_fuzz$slopes > 0 * lat_weight, na.rm = TRUE)
signif_pos_slope_areawt <- sum(out_fuzz$slopes > 0 & out_fuzz$signif < 0.05 * lat_weight, na.rm = TRUE)

# Convert to a data frame for ggplot2 plotting
ro = nrow(co2_fuzz)
co = ncol(co2_fuzz)
yr = dim(co2_fuzz)[3]
co2_fuzz_df <- tibble(
  flux = as.vector(co2_fuzz),
  lat = rep(seq_len(ro), times = co * yr),
  lon = rep(rep(seq_len(co), each = ro), times = yr),
  year = rep(seq_len(yr), each = ro * co),
  p = rep(as.vector(out_fuzz$signif), times = yr)
)

co2_fuzz_df %>% 
  filter(!is.na(p)) %>% 
  # pick a subset of grid cells for a readable plot
  distinct(lon, lat) %>% 
  sample_n(250) %>% 
  left_join(co2_fuzz_df, by = c("lon", "lat")) ->
  co2_fuzz_subsampled

co2_fuzz_subsampled %>% 
  ggplot(aes(year + 1990, flux, group = paste(lat, lon))) + 
  geom_line(color = "lightgrey") +
  xlab("Year") + ylab(expression(R[S]~(g~C~m^{-2}~yr^{-1}))) +
  geom_line(data = filter(co2_fuzz_subsampled, p < 0.05), color = "red", alpha = I(0.5)) ->
  fuzz_time_series
# save_agu_plot("fuzz_over_time.png")
```

Cells with _significant_ positive slope (observations with `r round(median_error * 100, 0)`% measurement error) = `r signif_pos_slope` or `r round(signif_pos_slope / ncells * 100, 0)`%.

Area with _significant_ positive slope = `r round(signif_pos_slope_areawt / ncells_areawt * 100, 0)`%.


# Next steps

Next: make a nice graph of change over time 
using a subset of data for readability
Convert array to data frame and plot rs versus time
with a line for each grid cell

# Simple: when would expect to see significance?

* We'd like to do this once for perfect data
* Once for data + interannual variability
* Once for data + iav + observational error

```{r simple, echo=FALSE}
set.seed(1234)

trend_emergence <- function(rd, theilsen = F) {
  Year <- seq_len(length(rd))
  trend_p <- rep(NA, length(rd))
  for(i in seq_along(trend_p)) {
    if(i > 2) {
      if(theilsen) {
        df <- tibble(Year = Year[1:i], rd = rd[1:i])
        suppressWarnings(m <- mblm::mblm(rd ~ Year, data = df))  # mblm doesn't like form below
      } else {
        m <- suppressWarnings(lm(rd[1:i] ~ Year[1:i]))
      }
      # Extract 2nd row (Year) and 4th column (Pr>[t] or Pr>|V|)
      trend_p[i] <- summary(m)$coefficients[2, 4]
    }
  }
  trend_p
}


# Temperature has risen 0.9 C in 40 years, more or less
dTdt <- round(0.9 / 40.0, 3)
q10 <- 2
R0 = 1.0
respdata <- tibble(Year = 1:100,
                   Temp = dTdt * Year,
                   Resp = R0 * q10 ^ (Temp / 10),
                   # This is interannual variability
                   Resp_iav = fuzz(Resp, 0.098),  # this is SRDB Rs_interannual_err
                   Resp_fuzz = fuzz(Resp_iav, median_error))

# Make a nice plot--first with ideal curve, then IAV, then observations
p <- ggplot(respdata, aes(Year, Resp)) + 
  geom_point(color = "grey") + 
  ylab("Respiration") + coord_cartesian(ylim = c(0.75, 1.5)) + 
  annotate("text", 10, 1.4, label = paste("Q10 =", q10)) + 
  annotate("text", 10, 1.3, label = paste("dT/dt =", dTdt))
save_agu_plot("01.png")
p <- p + geom_point(aes(y = Resp_iav))
save_agu_plot("02.png")
p <- p + geom_errorbar(aes(ymin = Resp_iav - Resp_iav * median_error,
                           ymax = Resp_iav + Resp_iav * median_error))
save_agu_plot("03.png")

save_agu_plot("04.png",
              p + geom_line(aes(y = Resp), color = "red", size = 2))

save_agu_plot("05.png",
              p + geom_line(aes(y = Resp), color = "pink", size = 2) +
                geom_line(aes(y = Resp_iav), color = "red", size = 2))

save_agu_plot("06.png",
              p + geom_line(aes(y = Resp), color = "pink", size = 2) +
                geom_line(aes(y = Resp_iav), color = "pink", size = 2) +
                geom_line(aes(y = Resp_fuzz), color = "red", size = 2))


do_sim <- function(i, respdata, error = 0.0) {
  # This is observational error
  respdata$Resp_fuzz <- fuzz(respdata$Resp_iav, error)
  respdata$trend_p <- trend_emergence(respdata$Resp_fuzz)
  respdata
}

results <- list()
library(parallel)
n_sims <- 100
results <- mclapply(seq_len(n_sims), do_sim, respdata, error = median_error)

results %>% 
  bind_rows %>% 
  group_by(Year) %>% 
  summarise(n = n(), 
            Temp = mean(Temp), 
            Resp = mean(Resp),
            Resp_iav_sd = sd(Resp_iav),
            Resp_iav = mean(Resp_iav),
            Resp_fuzz_sd = sd(Resp_fuzz),          
            Resp_fuzz = mean(Resp_fuzz), 
            trend_p_sd = sd(trend_p), 
            trend_p = mean(trend_p)) %>% 
  filter(!is.na(trend_p)) ->
  results_summary

p <- ggplot(results_summary, aes(Year, trend_p, color = trend_p < 0.05)) +
  geom_point() +
  geom_line(aes(y = Resp_fuzz)) +
  geom_line(aes(y = Resp), color = "grey") +
  geom_ribbon(aes(ymin = Resp_fuzz - Resp_fuzz_sd, 
                  ymax = Resp_fuzz + Resp_fuzz_sd, 
                  fill = trend_p < 0.05), color = NA, alpha = I(0.35)) +
  guides(color = FALSE, fill = FALSE) +
  annotate("text", 10, 1.5, label = paste("N =", n_sims)) +
  ylab("Theil-sen p-value   ///   Respiration")
print(p)
# save_agu_plot("simple_sim.png")
```

```{r, fig.height=8, fig.width=8}
# put figures together
plot_grid(fuzz_time_series, p,
          ncol = 1,
          labels = c("a", "b"))
```

```{r, fig.height=8, fig.width=8}
plot_grid(plot_IRGA_cv, plot_annual_cv) ->
  plot_cv
# put figures together
plot_grid(plot_signif_before, plot_cv, plot_signif_after,
          ncol = 1,
          labels = c("a", "b", "c"))
```

```{r}
cosore_q10 %>% 
  dplyr::select(R2_day) %>% 
  na.omit() %>% 
  ggplot(aes(x = R2_day)) + 
  geom_histogram(bins = 30, fill = "gray", col = "black")

cosore_q10 %>% 
  dplyr::select(R2_night) %>% 
  na.omit() %>% 
  ggplot(aes(x = R2_night)) + 
  geom_histogram(bins = 30, fill = "gray", col = "black")

cosore_q10 %>% 
  dplyr::select(R2_day) %>% 
  na.omit() %>% 
  filter(R2_day > 0.5)
```

We then analyzed the trend of annual RS time series for all grid cells (n=`r ncells`). The results tuen out that about `r signif_pos_slope`% cells (Figure S7, panel a) showed a significant (p<0.05) possitive trend. However, in the field experiment, measurement error should be considered. We obtained the annual RS interannual variability from the newest version of global soil respiration database (SRDB-V5). In addition, we obtained the instantaneous RS flux measurement variability from a community database for continuous soil respiration and other soil-atmosphere greenhouse gas flux data (COSORE23). The results show that RS interannual variability is about `r round(median_interann_cv,2)*100`% of annual RS, and instantaneous RS flux measurement variability is about `r round(median_error, 2)*100`% of measurement mean (Figure S7, panel b). When RS measurement variability was considered, only ~`r round (signif_pos_slope / ncells * 100, 0)`% (Figure S7, panel c) of cells showed a significant increase trend.

```{r}
MGRsD %>% 
  select(Study_number, Site_ID, Meas_Year) %>% 
  group_by(Study_number, Site_ID) %>% 
  count(Meas_Year) %>% 
  group_by(Study_number, Site_ID) %>% 
  summarise(n_year = n()) %>% 
  arrange(desc(n_year))
```




