---
title: "Time_for_warm_cosore"
author: "Jinshi"
date: "6/4/2020"
output: html_document
---

* Using cosore data, daytime as warm and night time as control treatment ******************************************************
```{r}
# Read cosore dataset
cosore <- readRDS("other_data/cosore_data.RDS")
```


```{r }
tibble::glimpse(csr_table(cosore, "description"))
desc <- csr_table(cosore, "description")
var_dataset <- desc$CSR_DATASET
which(var_dataset=='d20190415_VARNER')
# ds <- cosore$d20190517_MAURITZ # nobs = 2 or 3 if use daily timescale
```

# `r ds$description$CSR_DATASET`
```{r}
# i=2, no CSR_T5 information, using TCHmber?
i = 9
var_dataset[i]
# ds <- cosore$d20190409_ANJILELI
# cosore[CSR_DATASET == 'd20190517_MAURITZ',]
ds <- cosore$d20190517_MAURITZ
tibble::glimpse(ds$description)
# d <- ds$description
# diag <- ds$diagnostics
```

## Site information
```{r map, echo=FALSE}
library(sp)
library(leaflet)
df <- data.frame(lon = ds$description$CSR_LONGITUDE, lat = ds$description$CSR_LATITUDE)
coordinates(df) <- ~lon + lat
leaflet(df) %>% 
  addMarkers() %>% 
  addTiles(options = providerTileOptions(minZoom = 3, maxZoom = 3))
```

## Reference information
## Contributors
```{r contrib_table, echo=FALSE}
knitr::kable(unlist(ds$contributors), format = "html", col.names = c("Value")) %>% 
  kableExtra::kable_styling(full_width = FALSE, position = "left")
```

## Measurement information
**Instrument**: `r d$CSR_INSTRUMENT`
**File format**: `r d$CSR_FILE_FORMAT`
**Timestamp format**: `r d$CSR_TIMESTAMP_FORMAT`
**Timestamp timezone**: `r d$CSR_TIMESTAMP_TZ`
```{r msmt_table, echo=FALSE}
knitr::kable(ds$ports, format = "html") %>% 
  kableExtra::kable_styling(full_width = FALSE, position = "left")
```

## Column mapping
```{r mapping, echo=FALSE}
knitr::kable(ds$columns, format = "html") %>% 
  kableExtra::kable_styling(full_width = FALSE, position = "left")
```

## Data processing diagnostics
Info                |  Value
------------------- | ----
Records             | `r diag$CSR_RECORDS`
Records removed (error)     | `r diag$CSR_RECORDS_REMOVED_ERR`
Records removed (invalid timestamp)     | `r diag$CSR_RECORDS_REMOVED_TIMESTAMP`
Records removed (no flux)   | `r diag$CSR_RECORDS_REMOVED_NA`
Records (flux < `r diag$CSR_FLUX_LOWBOUND`)  | `r diag$CSR_RECORDS_REMOVED_TOOLOW`
Records (flux > `r diag$CSR_FLUX_HIGHBOUND`) | `r diag$CSR_RECORDS_REMOVED_TOOHIGH`
Columns dropped     | `r diag$CSR_COLUMNS_DROPPED`
Bad `Tchamber` values removed | `r diag$CSR_BAD_TCHAMBER`
Size                | `r format(object.size(ds), "Mb")`

**Flux summary**:

```{r flux-graphs}
if(is.data.frame(ds$data) & !FALSE) {
  print(summary(ds$data$CSR_FLUX))
  
  dsd <- subset(ds$data, !is.na(CSR_FLUX) & CSR_FLUX > 0)
  
  # flux over time
  p1 <- ggplot(dsd, aes(CSR_TIMESTAMP, CSR_FLUX, color = CSR_PORT)) + 
    geom_line() + facet_grid(CSR_PORT~., scales = "free_y")
  print(p1)
  
  p2 <- ggplot(dsd, aes(CSR_TIMESTAMP, CSR_FLUX, color = CSR_PORT)) +
    geom_point(size = 0.2) + scale_y_log10()
  print(p2)
  
  dsd %>% 
    mutate(CSR_PORT = as.factor(CSR_PORT),
           Month = month(CSR_TIMESTAMP)) %>% 
    group_by(CSR_PORT, Month) %>% 
    summarise(CSR_FLUX = mean(CSR_FLUX)) %>% 
    ggplot(aes(Month, CSR_FLUX, color = CSR_PORT, group = CSR_PORT)) + 
    geom_line() ->
    p3
  print(p3)
  # histogram
  p4 <- ggplot(dsd, aes(x = CSR_FLUX)) + geom_histogram(bins = 30)
  print(p4)
}
```


```{r}
# using dsd data to test day and night Q10 (use one site as an example)
dsd %>% mutate(CSR_T5 = CSR_TCHAMBER,
               Year = year(CSR_TIMESTAMP),
               Month = month(CSR_TIMESTAMP),
               Day_range = case_when(
                 day(CSR_TIMESTAMP) %in% 1:5 ~ 1,
                 day(CSR_TIMESTAMP) %in% 6:10 ~ 2,
                 day(CSR_TIMESTAMP) %in% 11:15 ~ 3,
                 day(CSR_TIMESTAMP) %in% 16:20 ~ 4,
                 day(CSR_TIMESTAMP) %in% 21:25 ~ 5,
                 TRUE ~ 6
               ),
               Day = day(CSR_TIMESTAMP),
               Hour = hour(CSR_TIMESTAMP),
               DayNight = case_when (
                 hour(CSR_TIMESTAMP) >= 19 | hour(CSR_TIMESTAMP) <= 6 ~ "Night",
                 TRUE ~ "Day" ) ) %>% 
  # filter (!is.na(dsd$CSR_T5)) %>% 
  arrange(CSR_PORT,Year,Month,Day) -> dsd
dsd %>% filter (!is.na(dsd$CSR_T5)) -> dsd
```


```{r}
dsd %>% filter (Year == 2010 & Month == 3 & Day ==12 & CSR_PORT == 1 & DayNight == 'Day') %>% nrow()
dsd %>% filter (Year == 2016 & Month == 4 & Day_range ==5 & CSR_PORT == 0 & DayNight == 'Night') %>% nrow()
```


```{r, include=FALSE}
outputs_ds9 <- DN_Q10 (dsd, var_dataset = var_dataset[i])
```


```{r, fig.width=10, fig.height=4}
outputs <- outputs_ds9
outputs %>% filter(!is.na(Q10_day) & !is.na(Q10_night)) -> outputs
min(outputs$day_TS - outputs$night_TS)
max(outputs$day_TS - outputs$night_TS)
mean(outputs$day_TS - outputs$night_TS)
Q10_DN_Comp (outputs)
```


```{r}
# night as control and daytime as warm? Time for warm?
ggplot(outputs) + aes(day_TS - night_TS) + geom_histogram(col = "black", fill = "gray", bins = 30) +
  geom_vline(xintercept = c(quantile (outputs$day_TS - outputs$night_TS, c(0.025, 0.5, 0.975), na.rm = T)),col = "red", linetype = "dotted", size = 1.5) +
  facet_wrap(~var_month.j.) +
  xlab(expression("Day-night T"[S]~"("~degree~C~")"))

ggplot(outputs) + aes(x="all", y=(day_TS - night_TS)) + geom_violin(col = "black", fill = "white", bins = 30) +
  facet_wrap(~var_month.j.) +
  geom_jitter(shape=16, position=position_jitter(0.2), col = 'gray') +
  xlab(expression("Day-night T"[S]~"("~degree~C~")"))

ggplot(outputs) + aes(Q10_day-Q10_night) + geom_histogram(col = "black", fill = "gray", bins = 30) +
  geom_vline(xintercept = c(quantile (outputs$Q10_day - outputs$Q10_night, c(0.025, 0.5, 0.975), na.rm = T)),col = "red", linetype = "dotted", size = 1.5) +
  facet_wrap(~var_month.j.) +
  xlab(expression("Day-night Q"[10]))

ggplot(outputs) + aes(x="all", y=(Q10_day - Q10_night)) + geom_violin(col = "black", fill = "white", bins = 30) +
  facet_wrap(~var_month.j.) +
  geom_jitter(shape=16, position=position_jitter(0.2), col = 'gray') +
  xlab(expression("Day-night T"[S]~"("~degree~C~")"))
```


```{r}
min(outputs$day_TS - outputs$night_TS)
```


```{r}
# test the relationship between Q10 diff and TS differ
outputs %>% mutate(Q10diff = Q10_day - Q10_night,
                   STdiff = day_TS - night_TS) %>%
  filter (STdiff > 0.5) %>%
  ggplot() +
  aes(x = STdiff, y = Q10diff) +
  geom_hex() +
  scale_fill_gradient(low = "gray", high = "blue") +
  geom_smooth(method = "lm") +
  xlab(expression("STday - STnight"~"("~degree~C~")")) +
  ylab(expression(dayQ[10]~"-"~nightQ[10]))

outputs %>% mutate(Q10diff = Q10_day - Q10_night,
                   STdiff = day_TS - night_TS) %>%
  filter (STdiff <= 0.5) %>%
  ggplot() +
  aes(x = STdiff, y = Q10diff) +
  geom_hex() +
  scale_fill_gradient(low = "gray", high = "blue") +
  geom_smooth(method = "lm") +
  xlab(expression("STday - STnight"~"("~degree~C~")")) +
  ylab(expression(dayQ[10]~"-"~nightQ[10]))
```


```{r}
# test Q10 differ under different ST differ gradient
outputs %>% mutate(Q10diff = Q10_day - Q10_night,
                   STdiff = day_TS - night_TS,
                   STgradient = case_when ( STdiff < 0.5 ~ "G1",
                                            TRUE ~ "G2")
                   ) %>% ggplot () + aes(x=STgradient, y=(Q10diff)) +
  geom_violin(col = "black", fill = "white") +
  facet_wrap(~var_month.j.) +
  geom_jitter(shape=16, position=position_jitter(0.2), col = 'gray') +
  ylab(expression("Q"[10]~diff))
```

```{r}
# test whether SM5 differ in night and day time
# ggplot (dsd) + aes (x = DayNight, y = CSR_SM5) + 
#   geom_violin(col = "black", fill = "white") +
#   facet_wrap(~Month) +
#   # geom_jitter(shape=16, position=position_jitter(0.2), col = 'gray') +
#   ylab(expression(SM~"( % )"))
```
.
```{r}
# compare Rh and Rs: port 1, 3, 5, 7, 9 11, 13, 15 are root exclusion sites
# outputs %>% mutate(Q10diff = Q10_day - Q10_night,
#                    RhRs = case_when ( var_port.k. %in% c(1,3,5,7,9,11,13,15) ~ "Rh",
#                                             TRUE ~ "Rs")
#                    ) %>% ggplot () + aes(x=RhRs, y=(Q10diff)) +
#   geom_violin(col = "black", fill = "white") +
#   facet_wrap(~var_month.j.) +
#   geom_jitter(shape=16, position=position_jitter(0.2), col = 'gray') +
#   ylab(expression("Q"[10]~diff))
```

**Temperature sensitivity**:
```{r tsensitivity}
tcols <- grep("^CSR_T(CHAMBER|[0-9]+)", names(ds$data))
if(length(tcols)) {
  fluxcol <- grep("CSR_FLUX", names(ds$data))
  results <- list()
  for(col in tcols) {
    x <- ds$data[fluxcol]
    x$Temperature <- pull(ds$data, col)#ds$data[,col]
    x$Which_temp <- names(ds$data)[col]
    results[[as.character(col)]] <- x
  }
  results <- bind_rows(results)
  
  p1 <- ggplot(results, aes(Temperature, CSR_FLUX)) + 
    geom_point(size = 0.2, alpha = I(0.25)) + 
    geom_smooth(method = "lm") +
    facet_wrap(~Which_temp, scales = "free")
  print(p1)
}
```